Paper TITLE

### 2016-08-04 code/Paper.Rmd
minor changes to Sri Plots

clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(ablmed, na.rm = T)) %>%
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + geom_line() +
  labs(x = "year", y = "Median Adjusted Income (per persons)", 
       title = "ABLmed by region")

>>>>

clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(ablmed, na.rm = T)) %>%
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + geom_line() + 
  scale_fill_manual(name = "Region", labels = regionNames)
  labs(x = "Year", y = "Median Adjusted Income (per persons)", 
       title = "ABLmed by region")
